Paper without a name

### 2014-05-30 Article.tex
Changes..
...

\subsection{Truncation}

For $n$ which is not a power of two, we construct $C_n^0$ by taking
$C_{2^{log_2(n)}}^0$ and keeping only boxes $(i, j)$ having $i, j < n$.

For example, $C_5^0$ can be generated from $C_8^0$ and by removing quite a lot
of the boxes. We obtain the following solution :

@@

For a box system $S = b_1 b_2 \dots b_p$, we construct the sets :

$$Perm_0 = { id }$$
$$Perm_k = (b_1 b_2 \dots b_k)(\left\{0,1\right\}^k)$$

@@

Each set $Perm_k$ is represented in memory as a bitset containing $n!$ bits, one
for each permutation of $\mathfrak{S}_n$. The isomorphism between the
permutations of $\mathfrak{S}_n$ and the numbers $\left\{0,1,\dots,n!-1\right\}$ is
constructed using the standard method described in (a citation).

@@

We can easily detect that $Perm_{k+1} = Perm_k$ when $ \# Perm_{k+1} = \# Perm_k$,
because $Perm_k \subset Perm_{k+1}$. When this condition is fulfilled, then we
know that the box $b_{k+1}$ is useless because it adds no permutation to the set
of generated permutations. We can therefore remove it from the box system.

By removing the boxes that this method detects as useless from the box system we
constructed in the previous paragraphs, we have constructed box systems that
generate all the permutations for $n \leq 13$ and that have $u_n$ boxes (ie the
conjectured optimum). We have not managed to run the test for $n \geq 14$,
because the required RAM exceeds 20Go, which is not a resource we have in our
possession.

>>>>

\subsection{Downscaling}

For $n$ which is not a power of two, we construct $C_n^0$ by taking
$C_{2^{\ceil{log_2(n)}}}^0$ and keeping only boxes $(i, j)$ having $i, j < n$.

For example, $C_5^0$ can be generated from $C_8^0$ and by removing 11 of the 20
boxes. We obtain the following solution :

@@

For a box system $C = b_1 b_2 \dots b_p$, we construct the sets :

$$Perm_k = (b_1 b_2 \dots b_k)(\left\{0,1\right\}^k)$$

These sets are recursively defined by :

$$Perm_0 = { id }$$
$$Perm_{k+1} = Perm_k \cup \left\{ \sigma \circ b_{k+1}, \; \sigma \in Perm_k
\right\}$$

@@

Each set $Perm_k$ is represented in memory as a bitset containing $n!$ bits, one
for each permutation of $\mathfrak{S}_n$. The isomorphism between the
permutations of $\mathfrak{S}_n$ and the numbers $\left\{0,1,\dots,n!-1\right\}$ is
constructed using the standard Lehmer code.

@@

We can easily detect that $Perm_{k+1} = Perm_k$ when $ |Perm_{k+1}| = |Perm_k|$,
because $Perm_k \subset Perm_{k+1}$. When this condition is fulfilled, then we
know that the box $b_{k+1}$ is useless because it adds no permutation to the set
of generated permutations. We can therefore remove it from the box system.

By removing the boxes that this method detects as useless from the box system we
constructed in the previous paragraphs, we have constructed box systems that
generate all the permutations for $n \leq 13$ and that have $u_n$ boxes (ie the
conjectured optimum). We note the simplified system for $n$ wires $C_n^1$. We
have not managed to run the test for $n \geq 14$, because the required RAM
exceeds 20Go, which is not a resource we have in our possession.

For example for $n=5$, we have :

$$C_5^0 = (0,1)(2,3)(0,2)(1,3)(0,4)(0,2)(1,3)(0,1)(2,3)$$
$$C_5^1 = (0,1)(2,3)(0,2)(1,3)(0,4)(0,2)(0,1)(2,3)$$

\begin{figure}
    \centering
    \begin{tabular}{|c|c|c|c|c|}
    \hline
    Number of wires $n$ & Size of $C_n^0$ & Size of $C_n^1$ & $opt_n$ &
	$u_n$ \\
    \hline
    2 & 1 & 1 & 1 & 1 \\
    3 & 3 & 3 & 3 & 3 \\
    4 & 6 & 5 & 5 & 5\\
    5 & 9 & 8 & 8 & 8\\
    6 & 12 & 11 & 11 & 11 \\
    7 & 15 & 14 &   & 14\\
    8 & 20 & 17 &   & 17\\
    9 & 25 & 21 &   & 21\\
    10 & 28 & 25 &   & 25\\
    11 & 31 & 29 &   & 29\\
    12 & 34 & 33 &   & 33\\
    13 & 39 & 37 &   & 37\\
    \hline
    \end{tabular}
    \caption{Minimum box count for small number of wires, checked experimentally}
    \label{box-count}
\end{figure}
